% Custom Site vs. Squarespace — Summary for Drew & Max
% Compile with: xelatex custom-vs-squarespace-summary.tex
\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.7in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{colortbl}
\usepackage{hyperref}
\hyphenpenalty=10000
\exhyphenpenalty=10000

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

% ── Colors ──────────────────────────────────────────────────────
\definecolor{wwsBlack}{HTML}{000000}
\definecolor{wwsDark}{HTML}{383838}
\definecolor{wwsLight}{HTML}{F4F4F2}
\definecolor{wwsGray}{HTML}{E0E0E0}
\definecolor{wwsAccent}{HTML}{FCD518}
\definecolor{secBg}{HTML}{F7F7F5}
\definecolor{greenGood}{HTML}{2E7D32}
\definecolor{redBad}{HTML}{C62828}

% ── Fonts ───────────────────────────────────────────────────────
\setmainfont{Inter}[
  Path=fonts/,
  Extension=.ttf,
  UprightFont=*,
  BoldFont=*,
  BoldFeatures={FakeBold=1.5},
  ItalicFont=*,
  ItalicFeatures={FakeSlant=0.2},
]
\newfontfamily\headingfont{CormorantGaramond}[
  Path=fonts/,
  Extension=.ttf,
  UprightFont=*,
  BoldFont=*,
  BoldFeatures={FakeBold=1.5},
]

% ── Section styling ─────────────────────────────────────────────
\newcommand{\sectionhead}[1]{%
  \vspace{10pt}%
  {\headingfont\Large\bfseries #1}\\[-3pt]%
  {\color{wwsAccent}\rule{\linewidth}{1.5pt}}%
  \vspace{2pt}%
}

\newcommand{\prositem}[1]{\item[\textcolor{greenGood}{\textbf{+}}] #1}
\newcommand{\consitem}[1]{\item[\textcolor{redBad}{\textbf{--}}] #1}

\begin{document}

% ── Header ──────────────────────────────────────────────────────
\begin{center}
{\headingfont\LARGE\bfseries Custom Site vs.\ Squarespace}\\[2pt]
{\color{wwsDark}\small A quick breakdown for Drew \& Max\quad|\quad March 2026\quad|\quad Prepared by Andrew}
\end{center}

\vspace{-2pt}
{\color{wwsGray}\rule{\linewidth}{0.5pt}}

% ── The Situation ───────────────────────────────────────────────
\sectionhead{Where Things Stand}

Your site is 29 static pages with images and a workaround booking flow (\$0 products added to a Squarespace cart). You don't use any Squarespace-only features. Your two external services---\textbf{Acuity Scheduling} and \textbf{Square Payments}---work on any platform. They're not tied to Squarespace and wouldn't change at all.

Moving to a custom site hosted on Vercel or Cloudflare Pages would cost \textbf{\textasciitilde\$10/year} (just the domain) vs.\ \textbf{\$300--700/year} on Squarespace. But the real argument isn't cost---it's \textbf{speed, flexibility, and protection}.

% ── Speed ───────────────────────────────────────────────────────
\sectionhead{Speed: Why Changes Get Faster}

I use an AI-powered coding tool (Claude Code) that can build, edit, and maintain websites extremely fast---but \textbf{it can't touch Squarespace}. Squarespace is a closed platform. Every change you request on Squarespace costs me 3--5$\times$ the time it would on a custom site.

\vspace{2pt}
\begin{tabularx}{\linewidth}{@{}p{3.8cm} X X@{}}
\toprule
\textbf{Task} & \textbf{On Squarespace} & \textbf{On Custom Site} \\
\midrule
Change colors/fonts site-wide & Click through every section & One command, done in seconds \\
Add a new studio set page & Copy page, edit every block & Duplicate template, auto-fill \\
Redesign the gallery & Limited to SQ gallery blocks & Any layout, full control \\
Add features (chat, automations) & \textcolor{redBad}{\textbf{Not possible}} & Built \& deployed same day \\
Fix something on all 29 pages & Edit each page one by one & One command updates all \\
\bottomrule
\end{tabularx}

% ── ADA ─────────────────────────────────────────────────────────
\sectionhead{ADA Compliance: Custom Is Safer}

You may have heard about serial ADA lawsuits---lawyers scan websites with automated tools and sue small businesses over accessibility failures (missing image descriptions, poor contrast, keyboard issues). \textbf{Over 4,000 federal cases were filed in 2024 alone}, and small businesses are the primary target.

The \textbf{risk of getting sued is the same} on either platform---serial plaintiffs scan the output, not the tech stack. But your ability to \textbf{fix issues} is dramatically better on a custom site:

\vspace{2pt}
\begin{tabularx}{\linewidth}{@{}p{3.8cm} X X@{}}
\toprule
& \textbf{Squarespace} & \textbf{Custom Site} \\
\midrule
Baseline accessibility & Some built-in support & WCAG 2.1 AA from day one \\
Control over fixes & Can't modify SQ's code & Full control over everything \\
Third-party code & SQ injects code you can't audit & You choose what's on the page \\
Ongoing compliance & Manual checks, no tooling & Claude Code audits \& fixes all pages in one pass \\
\bottomrule
\end{tabularx}

\vspace{4pt}
On Squarespace, some accessibility problems are \textbf{baked into the platform} and you literally cannot fix them.

% ── Services ────────────────────────────────────────────────────
\sectionhead{Your External Services Stay Put}

\begin{itemize}[nosep, leftmargin=1.2em]
\item \textbf{Acuity Scheduling} --- Works standalone. One embed line on the new site. Same links, same flow.
\item \textbf{Square Payments} --- Processed externally. Works anywhere. No change needed.
\end{itemize}

Nothing breaks. Nothing migrates. They just keep working.

% ── Cost ────────────────────────────────────────────────────────
\sectionhead{Cost Comparison}

\begin{tabularx}{\linewidth}{@{}X r r@{}}
\toprule
& \textbf{Squarespace (current)} & \textbf{Custom Site} \\
\midrule
Hosting & \$276--468/yr & \$0 \\
Domain & \textasciitilde\$20/yr & \textasciitilde\$10/yr \\
Acuity (if keeping) & \$240/yr & \$240/yr \\
\midrule
\textbf{Annual total} & \textbf{\$536--728} & \textbf{\$250} \\
\textbf{5-year total} & \textbf{\$2,680--3,640} & \textbf{\$1,250} \\
\bottomrule
\end{tabularx}

\vspace{4pt}
If you switch from Acuity to a free alternative (Cal.com), the custom site drops to \textbf{\textasciitilde\$10/year}.

% ── What You'd Lose ────────────────────────────────────────────
\sectionhead{The One Tradeoff}

You'd lose \textbf{Squarespace's visual drag-and-drop editor}. If you need a text or image change:

\begin{enumerate}[nosep, leftmargin=1.5em]
\item Text me---I push the change in under 5 minutes (Claude Code makes this trivial).
\item Or we set up a free browser-based CMS so you can edit content yourselves.
\end{enumerate}

If you rarely edit the site yourselves (which seems to be the case), this doesn't matter.

% ── Timeline ────────────────────────────────────────────────────
\sectionhead{Timeline}

We already have a 4-page mockup built with the design system, fonts, and logo. Remaining work: \textbf{\textasciitilde16--24 hours} to finish all pages, set up hosting, migrate images, and go live. Realistically \textbf{1--2 weeks} of part-time sessions.

% ── Bottom Line ─────────────────────────────────────────────────
\vspace{6pt}
\begin{tikzpicture}
\fill[wwsLight, rounded corners=4pt] (0,0) rectangle (\linewidth, 1.4);
\node[anchor=west, text width=\linewidth-1cm] at (0.5, 0.7) {%
  {\headingfont\large\bfseries Bottom Line:}\quad
  {\small You're paying \$300--700/yr for a platform that slows down every change, can't be automated, limits your features, and gives you less control over ADA compliance. The migration is straightforward and your external services don't change.}%
};
\end{tikzpicture}

\end{document}
